---
title: "Jaccard index"
author: "Enrico Gaffo"
date: "`r Sys.Date()`"
output: 
  html_document: 
    toc: yes
    toc_float: yes
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
library(data.table)
library(patchwork)
# install.packages("ggdendro")
library(ggdendro)
library(ggplot2)
library(scales)
library(viridis)
library(dendsort)
library(seriation)

library(BiocParallel)
library(SummarizedBenchmark)

library(svglite)

library(ComplexHeatmap)
library(circlize)
library(gridtext)
library(colorspace)

outdir <- "jaccard"
dir.create(path = outdir, showWarnings = F, recursive = T)

knitr::opts_chunk$set(echo = TRUE, 
                      fig.path = file.path(outdir, "Figs/"), 
                      dev = c("png", "svglite", "pdf"))
```

# Method names

```{r}
source("method_types_and_colors.R")
plot_base_method_color_text_rot <- plot_base_method_color_text
plot_base_method_color_text <- plot_base_method_color_text_v
plot_base_method_type_tiles <- plot_base_method_type_tiles_v
```

# Jaccard

The Jaccard index (or similarity) gives the size of the intersection divided by the size of the union of the sample sets. The Jaccard distance, which measures dissimilarity between sample sets, is complementary to the Jaccard coefficient and is obtained by subtracting the Jaccard coefficient from 1, or, equivalently, by dividing the difference of the sizes of the union and the intersection of two sets by the size of the union.  

Here, the Jaccard similarity is computed on the DECs called by each method at 5% FDR.    
Therefore, 

```{r}
# sumBench_perf_metrics_qs_files <- file.path("benchmark_results", 
#                                             c("DM1", "IPF", "MS", "IDC"), 
#                                             "sumBench_perf_metrics.qs")
# 
# names(sumBench_perf_metrics_qs_files) <- sub("benchmark_results/", "",
#                                              dirname(sumBench_perf_metrics_qs_files))

# benchmark_results_dirs <- c("benchmark_results", "benchmark_results_2")
benchmark_results_dirs <- c("benchmark_results")
sumBench_perf_metrics_qs_files <- 
  unlist(lapply(X = benchmark_results_dirs,
                FUN = file.path, 
                file.path(c("DM1", "IPF", "MS", "IDC"), 
                          "sumBench_perf_metrics.qs")))
names(sumBench_perf_metrics_qs_files) <- 
  sub("benchmark_results", "",
      dirname(sumBench_perf_metrics_qs_files))

## check if some files are missing and fix the list
exist_files <- sapply(sumBench_perf_metrics_qs_files, file.exists)
warning("Missed files:\n", paste0(sumBench_perf_metrics_qs_files[!exist_files],
                                  collapse = "\n"))
sumBench_perf_metrics_qs_files <- sumBench_perf_metrics_qs_files[exist_files]

ncpus <- BiocParallel::multicoreWorkers()
bpparam <- BiocParallel::SerialParam()

sbL <- bplapply(sumBench_perf_metrics_qs_files, 
                qs::qread, 
                nthreads = ncpus,  #multicoreWorkers()
                BPPARAM = bpparam)

adj_pval_deind_dt <- 
      rbindlist(lapply(sbL, 
                       function(y) {
                         rbindlist(lapply(y,
                                          function(x) {
                                            melt(data.table(true_val = as.integer(groundTruths(x)[["adj_pv"]]),
                                                            assays(x)[["adj_pv"]]),
                                                 id.vars = "true_val",
                                                 value.name = "preds",
                                                 variable.name = "Method")
                                          }),
                                   idcol = "Dataset")
                       }), 
                idcol = "Source_ds")

# adj_pval_deind_dt[is.na(preds), preds := 1]

adj_pval_deind_dt[, c("SetSize", "MZP", "DsType", "DsId") := tstrsplit(Dataset, "_"), 
                  by = Dataset]

adj_pval_deind_dt[, Source_ds := gsub("^[^/]*/", "", Source_ds), by = Source_ds]
```

```{r}
ds_names <- c("DM1", "IPF", "MS", "IDC")

padj <- adj_pval_deind_dt[MZP == "bulk" & DsType == "de"]
```

```{r}
padj[, Gid := seq_along(preds), by = .(Source_ds, Dataset, Method)]
padj[is.na(preds), preds := 1]

padj_l <- split(padj, drop = F, by = c("Source_ds", "Dataset"), flatten = F)

## compute dists for 5% FDR
jaccard_dists <- 
    rbindlist(lapply(padj_l, function(dataset){
        
        rbindlist(lapply(dataset, function(simds){
            
            mt <- as.matrix(data.frame(dcast(simds[, .(Method, preds, Gid)], 
                                             Gid ~ Method, 
                                             value.var = "preds", 
                                             fill = 0), 
                                       row.names = "Gid"))
            as.data.table(as.matrix(dist(x = t(mt) <= .05, method = "binary")),
                          keep.rownames = "Method")
        }), 
        idcol = "Dataset", fill = T)
    }), 
    idcol = "Source_ds", fill = T)

## compute dists for 10% FDR
jaccard_dists_0.1 <- 
    rbindlist(lapply(padj_l, function(dataset){
        
        rbindlist(lapply(dataset, function(simds){
            
            mt <- as.matrix(data.frame(dcast(simds[, .(Method, preds, Gid)], 
                                             Gid ~ Method, 
                                             value.var = "preds", 
                                             fill = 0), 
                                       row.names = "Gid"))
            as.data.table(as.matrix(dist(x = t(mt) <= .1, method = "binary")),
                          keep.rownames = "Method")
        }), 
        idcol = "Dataset", fill = T)
    }), 
    idcol = "Source_ds", fill = T)

## compute dists for 1% FDR
jaccard_dists_0.01 <-
    rbindlist(lapply(padj_l, function(dataset){

        rbindlist(lapply(dataset, function(simds){

            mt <- as.matrix(data.frame(dcast(simds[, .(Method, preds, Gid)],
                                             Gid ~ Method,
                                             value.var = "preds",
                                             fill = 0),
                                       row.names = "Gid"))
            as.data.table(as.matrix(dist(x = t(mt) <= .01, method = "binary")),
                          keep.rownames = "Method")
        }),
        idcol = "Dataset", fill = T)
    }),
    idcol = "Source_ds", fill = T)

avg_jaccard_dists <-
    melt(jaccard_dists, 
         id.vars = c("Source_ds", "Dataset", "Method"), 
         variable.name = "Method2", 
         value.name = "Jdist")[, c("SetSize", "MZP", "DsType", 
                                   "DsId") := tstrsplit(Dataset, "_"), 
                               by = Dataset][, .(AvgJDist = mean(Jdist)), 
                                             by = .(Source_ds, SetSize, MZP, DsType, 
                                                    Method, Method2)]

avg_jaccard_dists_0.1 <-
    melt(jaccard_dists_0.1, 
         id.vars = c("Source_ds", "Dataset", "Method"), 
         variable.name = "Method2", 
         value.name = "Jdist")[, c("SetSize", "MZP", "DsType", 
                                   "DsId") := tstrsplit(Dataset, "_"), 
                               by = Dataset][, .(AvgJDist = mean(Jdist)), 
                                             by = .(Source_ds, SetSize, MZP, DsType, 
                                                    Method, Method2)]

avg_jaccard_dists_0.01 <-
    melt(jaccard_dists_0.01, 
         id.vars = c("Source_ds", "Dataset", "Method"), 
         variable.name = "Method2", 
         value.name = "Jdist")[, c("SetSize", "MZP", "DsType", 
                                   "DsId") := tstrsplit(Dataset, "_"), 
                               by = Dataset][, .(AvgJDist = mean(Jdist)), 
                                             by = .(Source_ds, SetSize, MZP, DsType, 
                                                    Method, Method2)]
```

```{r, warning=FALSE}
avg_jaccard_dists_l <- split(avg_jaccard_dists, by = c("Source_ds", "SetSize"), flatten = F, keep.by = F)

method_names <- sort(unique(avg_jaccard_dists_l$DM1$N10$Method))
# method_colors <- setNames(hue_pal()(length(method_names)), method_names)

# x <- avg_jaccard_dists_l$DM1$N10
# ggdendrogram(hclust(as.dist(data.frame(dcast(setSize, 
#                                              Method ~ Method2, 
#                                              value.var = "AvgJDist"), 
#                                        row.names = "Method"))))

ggd_l <- 
    lapply(avg_jaccard_dists_l, function(ds){
        lapply(ds, function(setSize){
            ddata <- 
                dendro_data(as.dendrogram(dendsort(hclust(as.dist(data.frame(dcast(setSize, 
                                                                          Method ~ Method2, 
                                                                          value.var = "AvgJDist"), 
                                                                    row.names = "Method"))), 
                                                   isReverse = T)), 
                            type = "rectangle")
            
            ggplot(segment(ddata), aes(x = x, y = y)) +
                geom_segment(aes(xend = xend, yend = yend)) +
                scale_x_continuous(name = NULL, breaks = label(ddata)$x, 
                                   labels = label(ddata)$label, 
                                   position = "top") +
                scale_y_reverse(name = "Jaccard distance", expand = c(0, 0.01)) +
                coord_flip() +
                theme_minimal() +
                theme(axis.text.y = element_text(color = method_colors[label(ddata)$label]),
                      panel.grid.major.x = element_blank(),
                      panel.grid.minor.x = element_blank(),
                      panel.grid.major.y = element_blank(),
                      panel.grid.minor.y = element_blank())
        })
        
    })
```

```{r, fig.height=20, fig.width=10}
# gg_rows <- lapply(setNames(ds_names, nm = ds_names), 
#                   function(x, ggd_l){
#                       ggd_l[[x]]$N03 + ggtitle(paste(x, "N03")) +
#                           ggd_l[[x]]$N05 + ggtitle(paste(x, "N05")) +
#                           ggd_l[[x]]$N10 + ggtitle(paste(x, "N10"))
#                   }, 
#                   ggd_l = ggd_l)
# 
# gg_rows$DM1 / gg_rows$IPF / gg_rows$MS / gg_rows$IDC
```

## Average Jaccard per set size

```{r, warning=FALSE, fig.width=9, fig.height=5.5}
plots <- 
    lapply(split(avg_jaccard_dists[, .(AvgJDist = mean(AvgJDist)), 
                                   by = .(SetSize, MZP, DsType, Method, Method2)], 
                 by = c("SetSize"), flatten = F, keep.by = F), 
           function(setSize){
               # ddata <- 
               #     dendro_data(as.dendrogram(dendsort(hclust(as.dist(data.frame(dcast(setSize, 
               #                                                               Method ~ Method2, 
               #                                                               value.var = "AvgJDist"), 
               #                                                         row.names = "Method")))), 
               #                               isReverse = T), 
               #                 type = "rectangle")
               ddata <- 
                   dendro_data(as.dendrogram(seriate(as.dist(data.frame(dcast(setSize, 
                                                                              Method ~ Method2, 
                                                                              value.var = "AvgJDist"), 
                                                                        row.names = "Method")), 
                                                     method = "GW_complete")[[1]]), 
                               type = "rectangle")
               
               plot <-
                   ggplot(segment(ddata), aes(x = y, y = x)) +
                   geom_segment(aes(yend = xend, xend = yend)) +
                   scale_y_continuous(name = NULL, 
                                      breaks = label(ddata)$x, 
                                      labels = label(ddata)$label, 
                                      position = "right", 
                                      expand = c(0, 0)) +
                   scale_x_reverse(name = "Jaccard distance", expand = c(0, 0)) +
                   coord_cartesian(ylim = c(.5, length(unique(label(ddata)$label))+.5)) +
                   theme_minimal() +
                   theme(axis.text.y = element_text(color = method_colors[label(ddata)$label]),
                         panel.grid.major.x = element_blank(),
                         panel.grid.minor.x = element_blank(),
                         panel.grid.major.y = element_blank(),
                         panel.grid.minor.y = element_blank())
               
               list(ddata = ddata, plot = plot)
           })

# plots$N03$plot  + 
#   ggtitle("N03") + 
#   theme(axis.text.x = element_text(angle = -35, hjust = .5, vjust = -1)) +
#   plots$N05$plot + 
#   ggtitle("N05") + 
#   theme(axis.text.x = element_text(angle = -35, hjust = .5, vjust = -1)) +
#   plots$N10$plot + 
#   ggtitle("N10") + 
#   theme(axis.text.x = element_text(angle = -35, hjust = .5, vjust = -1))


wrap_plots(
  wrap_plots(plots$N03$plot + 
               theme(axis.text.y = element_blank(),
                     axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)), 
             plot_base_method_color_text + 
               scale_y_discrete(limits = label(plots$N03$ddata)$label) &
               ggtitle("N03"), 
             nrow = 1, widths = c(.6, 1)), 
  wrap_plots(plots$N05$plot + 
               theme(axis.text.y = element_blank(),
                     axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)), 
             plot_base_method_color_text + 
               scale_y_discrete(limits = label(plots$N05$ddata)$label) &
               ggtitle("N05"), 
             nrow = 1, widths = c(.6, 1)),
  wrap_plots(plots$N10$plot + 
               theme(axis.text.y = element_blank(),
                     axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)), 
             plot_base_method_color_text + 
               scale_y_discrete(limits = label(plots$N10$ddata)$label) &
               ggtitle("N10"), 
             nrow = 1, widths = c(.6, 1)),
  nrow = 1)
```

### N05  

```{r, fig.height=5.5, fig.width=4.5}
plots_avg_jdn <- plots
avg_jdn05 <- plots$N05$plot

method_order <- label(plots$N05$ddata)$label

## plot the average rank tile plot instead of the mean performance
avg_jdn05_dendro_wrap <- 
    wrap_plots(avg_jdn05 + 
                   theme(axis.text.x = element_text(angle = 90, hjust = 1),
                         axis.text.y = element_blank(),
                         plot.margin = margin(0, 0, 0, 0, "lines")),
               plot_base_method_type_tiles +
                   scale_y_discrete(limits = method_order) +
                   theme(plot.background = element_blank(),
                         plot.margin = margin(0, 0, 0, 0, "lines")),
               plot_base_method_color_text +
                   scale_y_discrete(limits = method_order) +
                   theme(plot.margin = unit(c(0, 0, 0, 0), "lines")), 
               nrow = 1, guides = "collect",
               widths = c(.4, .1, 1)) & 
    theme(legend.position = "top",
          legend.key.size = unit(.7, "lines"),
          panel.spacing.x = unit(0, "lines"),
          panel.grid.minor = element_blank(),
          # plot.margin = margin(0.1, 0.1, 0.1, 0, "lines"),
          text = element_text(size = 10), 
          plot.tag = element_text(hjust = -1, vjust = -1, size = 12))

# avg_jdn05_dendro_wrap
```

```{r, fig.height=5.5, fig.width=4.5}
top_avg_jdn05_dendro_wrap <- 
    wrap_plots(avg_jdn05 + 
                   coord_flip() +
                   scale_x_continuous(name = "Jaccard distance") +
                   theme(axis.text.y = element_text(color = "black"),
                         axis.text.x = element_blank(),
                         plot.margin = margin(0, 0, 0, 0, "lines")),
               plot_base_method_type_tiles +
                   coord_flip() +
                   scale_y_discrete(limits = method_order) +
                   theme(plot.background = element_blank(),
                         plot.margin = margin(0, 0, 0, 0, "lines")),
               plot_base_method_color_text_rot +
                   scale_x_discrete(limits = method_order) +
                   theme(#text = element_text(angle = 90),
                         plot.margin = unit(c(0, 0, 0, 0), "lines")), 
               ncol = 1, guides = "collect",
               heights = c(1, .1, 1.5)) & 
    theme(legend.position = "top",
          legend.key.size = unit(.7, "lines"),
          panel.spacing.x = unit(0, "lines"),
          panel.grid.minor = element_blank(),
          # plot.margin = margin(0.1, 0.1, 0.1, 0, "lines"),
          text = element_text(size = 10), 
          plot.tag = element_text(hjust = -1, vjust = -1, size = 12))

# top_avg_jdn05_dendro_wrap
```

### N05 heatmap

```{r, fig.height=5.5, fig.width=5.5}
plot_dt <- avg_jaccard_dists[, .(AvgJDist = mean(AvgJDist)), 
                             by = .(SetSize, Method, 
                                    Method2)][SetSize == "N05"]

plot_dt[Method == Method2, AvgJDist := NA]
# method_order <- sort(method_types$Method)
method_order <- label(plots$N05$ddata)$label

## compute the lower mat triangle pairs and erase the corresponding plot
halfmat <- as.matrix(data.frame(dcast(plot_dt, Method ~ Method2, 
                                      value.var = "AvgJDist"), 
                                row.names = "Method"))[method_order, method_order]
halfmat[lower.tri(halfmat, diag = T)] <- NA

halfmat_m <- melt(data.table(halfmat, keep.rownames = "method1"), 
                  id.vars = "method1", variable.name = "method2",
                  value.name = "concordance")[method1 != method2]
na_pairs <- halfmat_m[is.na(concordance), paste(method1, method2)]

plot_dt[, pairname := paste(Method, Method2)]
plot_dt[pairname %in% na_pairs, AvgJDist := NA]

# seqpal <- "YlGnBu"
seqpal <- "YlOrRd"

n05_halfheat_plot <- 
    ggplot(plot_dt, aes(x = Method, y = Method2, 
                        color = 1 - AvgJDist,
                        size = 1 - AvgJDist,
                        fill = 1- AvgJDist)) +
    # geom_tile() +
    geom_point(shape = 21) +
    coord_fixed() +
    labs(x = NULL, y = NULL) +
    scale_size("Jaccard similarity", range = c(0, 3), guide = "none") +
    # scale_fill_viridis_c(option = "B", end = .98, direction = 1) +
    # scale_color_viridis_c(option = "B", end = .98, direction = 1) +
    scale_fill_distiller("Jaccard similarity", 
                         direction = 1, na.value = "white", palette = seqpal) +
    scale_color_distiller("Jaccard similarity", 
                          direction = 1, na.value = "white", palette = seqpal) +
    guides(color = guide_colorbar(title.position = "top", title.hjust = .5, 
                                  frame.colour = "black"),
           fill  = guide_colorbar(title.position = "top", title.hjust = .5, 
                                  frame.colour = "black")) +
    scale_x_discrete(limits = method_order,
                     labels = data.frame(method_labels_table, row.names = "Method")[method_order, "MethodLabel"],
                     position = "top") +
    scale_y_discrete(limits = method_order,
                     labels = data.frame(method_labels_table, row.names = "Method")[method_order, "MethodLabel"]) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 90, hjust = 0, vjust = .5, color = method_colors[method_order]),
          axis.text.y = element_text(color = method_colors[method_order]),
          legend.position = c(-.2, 1.2),#"bottom",
          legend.direction = "horizontal", legend.text = element_text(angle = 90, hjust = 1),
          text = element_text(size = 9),
          panel.grid = element_blank())

# n05_halfheat_plot
```

### N05 heatmap + dendro

```{r, fig.width=10.5, fig.height=7}
# # design <- "#A
# #            BC"
# # 
# # wrap_plots(top_avg_jdn05_dendro_wrap &
# #                theme(legend.position = "none",
# #                      plot.margin = margin(0, -1, 0, 0)),
# #            avg_jdn05_dendro_wrap &
# #                theme(legend.position = "botom",
# #                      plot.margin = margin(0, -1, 0, 0)),
# #            n05_halfheat_plot &
# #                theme(legend.position = "bottom",
# #                      axis.text.y = element_blank(),
# #                      axis.text.x = element_blank(),
# #                      plot.margin = margin(0, 0, 0, 0)),
# #            widths = c(1.75, 2),
# #            design = design)
# 
# wrap_plots(avg_jdn05_dendro_wrap +
#                theme(#legend.position = "botom",
#                      plot.margin = margin(0, 0, 0, 0),
#                      plot.background = element_blank()),
#            n05_halfheat_plot +
#                theme(#legend.position = "bottom",
#                      axis.text.y = element_blank(), 
#                      # axis.text.x = element_blank(), 
#                      plot.margin = margin(0, 0, 0, 0)),
#            nrow = 1, 
#            widths = c(1.75, 2)) &
#   theme(plot.background = element_rect(fill = "transparent", colour = NA))
```

### Complex Hetmap

```{r, fig.width=11, fig.height=11}
# https://jokergoo.github.io/ComplexHeatmap-reference/book/a-single-heatmap.html#cell-fun

plot_dt <- avg_jaccard_dists[, .(AvgJDist = mean(AvgJDist)), 
                             by = .(SetSize, Method, 
                                    Method2)][SetSize == "N05"]

plot_dt[Method == Method2, AvgJDist := NA]

## compute the lower mat triangle pairs and erase the corresponding plot
jdistmat <- as.matrix(data.frame(dcast(plot_dt, Method ~ Method2, 
                                       value.var = "AvgJDist"), 
                                 row.names = "Method"))[sort(method_names), 
                                                        sort(method_names)]

jsimmat <- 1 - jdistmat

jdistmat[is.na(jdistmat)] <- 0
met_ord_so <- seriate(x = as.dist(jdistmat), method = "GW_complete")

method_order <- data.frame(labels = met_ord_so[[1]]$labels, 
                           x = met_ord_so[[1]]$order, 
                           row.names = met_ord_so[[1]]$labels)
method_order <- method_order[method_order$x, ]

# colors_vector <- c("yellow", "orange", "red")
colors_vector <- sequential_hcl(n = 3, palette = "OrYel", rev = T)

col_fun = circlize::colorRamp2(c(0, .5, 1), colors_vector)

## this is just to control that the final plot will keep the correct clustering
# Heatmap(jsimmat, 
#         name = "Jaccard\nsimilarity", 
#         col = col_fun, 
#         rect_gp = gpar(type = "none"), 
#         cell_fun = function(j, i, x, y, width, height, fill) {
#             grid.circle(x = x, y = y, 
#                         r = jsimmat[j, i]/2 * min(unit.c(width,
#                                                          height)), 
#                         gp = gpar(fill = col_fun(jsimmat[j, i]), 
#                                   col = NA))
#         }, 
#         cluster_rows = as.dendrogram(met_ord_so[[1]]),
#         cluster_columns = as.dendrogram(met_ord_so[[1]]),
#         # cluster_rows = F,
#         # cluster_columns = F,
#         show_row_names = T, 
#         show_column_names = T)

jsimmat <- jsimmat[method_order$label, method_order$label]
jsimmat[upper.tri(jsimmat, diag = T)] <- NA
jsimmat <- jsimmat[method_names, method_names]

method_labels <- data.frame(method_labels_table, row.names = "Method")[method_order$label, , drop = F]
method_labels_v <- setNames(method_labels$MethodLabel, nm = rownames(method_labels))

# `col = col_fun` here is used to generate the legend
jsh <- Heatmap(jsimmat, 
               name = "Jaccard\nsimilarity", 
               col = col_fun, 
               rect_gp = gpar(type = "none"), 
               cell_fun = function(j, i, x, y, width, height, fill) {
                 if(!is.na(jsimmat[i, j])) {
                   # grid.rect(x = x, y = y, width = width, height = height, 
                   #           gp = gpar(col = "grey", fill = NA))
                   grid.circle(x = x, y = y, 
                               r = jsimmat[i, j]/2 * min(unit.c(width,
                                                                height)), 
                               gp = gpar(fill = col_fun(jsimmat[i, j]), 
                                         col = NA))
                 }
               }, 
               row_names_side = "left", 
               column_dend_side = "bottom", 
               width = unit(10, "cm"), 
               height = unit(10, "cm"),
               heatmap_legend_param = list(direction = "horizontal"), 
               row_labels = gt_render(method_labels_v[rownames(jsimmat)]),
               row_names_gp = gpar(col = method_colors[rownames(jsimmat)], fontsize = 9),
               column_labels = gt_render(method_labels_v[rownames(jsimmat)]),
               column_names_gp = gpar(col = method_colors[rownames(jsimmat)], fontsize = 9),
               cluster_rows = as.dendrogram(met_ord_so[[1]]),
               cluster_columns = as.dendrogram(met_ord_so[[1]]),
               show_row_names = T, 
               show_column_names = T)

draw(jsh, heatmap_legend_side = "top")
```

### N10 @ 10%FDR

```{r, fig.height=5.5, fig.width=4.5}
n10fdr10_avg_jaccard_dists <- 
    avg_jaccard_dists_0.1[SetSize == "N10",
                          .(AvgJDist = mean(AvgJDist)), 
                          by = .(SetSize, MZP, DsType, Method, Method2)]

n10fdr10_ddata <- 
    dendro_data(as.dendrogram(dendsort(hclust(as.dist(data.frame(dcast(n10fdr10_avg_jaccard_dists, 
                                                                       Method ~ Method2, 
                                                                       value.var = "AvgJDist"), 
                                                                 row.names = "Method")))), 
                              isReverse = T), 
                type = "rectangle")

n10fdr10_plot <-
    ggplot(segment(n10fdr10_ddata), aes(x = y, y = x)) +
    geom_segment(aes(yend = xend, xend = yend)) +
    scale_y_continuous(name = NULL, 
                       breaks = label(n10fdr10_ddata)$x, 
                       labels = label(n10fdr10_ddata)$label, 
                       position = "right", 
                       expand = c(0, 0)) +
    scale_x_reverse(name = "Jaccard distance", expand = c(0, 0)) +
    coord_cartesian(ylim = c(.5, length(unique(label(n10fdr10_ddata)$label))+.5)) +
    theme_minimal() +
    theme(axis.text.y = element_text(color = method_colors[label(n10fdr10_ddata)$label]),
          panel.grid.major.x = element_blank(),
          panel.grid.minor.x = element_blank(),
          panel.grid.major.y = element_blank(),
          panel.grid.minor.y = element_blank())

wrap_plots(n10fdr10_plot + 
               theme(axis.text.x = element_text(angle = 90, hjust = 1),
                     axis.text.y = element_blank(),
                     plot.margin = margin(0, 0, 0, 0, "lines")),
           plot_base_method_type_tiles +
               scale_y_discrete(limits = label(n10fdr10_ddata)$label) +
               theme(plot.background = element_blank(),
                     plot.margin = margin(0, 0, 0, 0, "lines")),
           plot_base_method_color_text +
               scale_y_discrete(limits = label(n10fdr10_ddata)$label) +
               theme(plot.margin = unit(c(0, 0, 0, 0), "lines")), 
           nrow = 1, guides = "collect",
           widths = c(1, .1, 1.5)) & 
    theme(legend.position = "top",
          legend.key.size = unit(.7, "lines"),
          panel.spacing.x = unit(0, "lines"),
          panel.grid.minor = element_blank(),
          # plot.margin = margin(0.1, 0.1, 0.1, 0, "lines"),
          text = element_text(size = 10), 
          plot.tag = element_text(hjust = -1, vjust = -1, size = 12))
```

# Session info

```{r}
sessionInfo()
```

