---
title: "Simulations with SPsimSeq"
author: "Enrico Gaffo"
date: "`r Sys.Date()`"
output: 
  html_document: 
    toc: yes
    toc_float: yes
    code_folding: hide
editor_options: 
  chunk_output_type: console
params:
  outdir: "../../../R/simulations/semiparametric/simdata"
  input_dataset_bjr_file: "../../../data/DM1_unfiltered_CirComPara2_circbjr.csv"
  input_dataset_meta_file: "../../../data/DM1_meta.csv"
  n_sims: 3
  max_circrrnas: 1000
  dec_fraction: 0.1
---

```{r}
## parameters to simulate the data sets
## number of data sets to simulate
n.sims <- params$n_sims
## number of circRNAs to simulate
Ncircrnas <- params$max_circrrnas #10000 #5000
## fraction of DECs
fracDECs <- params$dec_fraction

seed.num <- 2021
set.seed(seed.num)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# load required libraries
library(data.table)
library(SPsimSeq)
library(qs)
library(BiocParallel)
library(ggplot2)
library(scales)
library(DT)
library(edgeR)
```

```{r}
## load utility functions
source("../../../R/utils/fun_SPsimSeq.R")
source("../../../R/utils/sample_circs.R")
```

```{r}
dir.create(path = params$outdir, showWarnings = F, recursive = T)
```

```{r}
## root path from project dir
# outdir <- "../../../R/simulations/semiparametric/simdata"
# dir.create(path = outdir, recursive = T)

## names of output files
# source_dataset_qs <- file.path(outdir, "DM1_trimmed_source_dataset.qs")
source_dataset_qs <- file.path(params$outdir, "DM1_trimmed_source_dataset.qs")
simulated_datasets_qs <- file.path(params$outdir, "DM1_trimmed_simulated_datasets.qs")

# data.dir <- "../../../data"
# input_dataset_bjr_file <- file.path(data.dir, "DM1_unfiltered_CirComPara2_circbjr.csv")
# input_dataset_meta_file <- file.path(data.dir, "DM1_meta.csv")
```

# The source data set

Load the original data and make a basic filtering  

```{r}
# load the original data
counts_mt <- as.matrix(data.frame(fread(params$input_dataset_bjr_file), 
                                  row.names = "circ_id"))
group_dt <- fread(params$input_dataset_meta_file)
group_df <- data.frame(group_dt, 
                       row.names = "sample_id")
```

Data have `r nrow(counts_mt)` circRNAs.  

Samples partitioned between conditions  

```{r}
cond_parts <- group_dt[, .N, by = condition][, Frac := N/sum(N)][]
cond_parts
```

```{r}
min_samples <- 3
# remove genes with insufficient expression (important step to avoid bugs)
counts_mt <- counts_mt[rowSums(counts_mt > 0) >= min_samples, ]
```

Filtered data have `r nrow(counts_mt)` circRNAs (BJR > 0 in at least `r min_samples` samples).  

```{r}
lib_sizes <- apply(counts_mt, 2, sum)[rownames(group_df)]
lib_size_dt <- data.table(group_df, 
                          Lib_size = lib_sizes, 
                          keep.rownames = "Sample")
```

## Library size of samples

```{r}
## compute sample similarity according to library size
sample_clust_by_libsize <- 
  hclust(d = dist(x = lib_sizes, method = "euclidean"), 
         method = "complete")

Nclust_libsize <- 4
```

```{r}
sample_libsize_clust_dt <- 
  merge(data.table(Sample = sample_clust_by_libsize$labels, 
                   Corder = sample_clust_by_libsize$order,
                   LibGroup = cutree(tree = sample_clust_by_libsize, 
                                     k = Nclust_libsize)),
        lib_size_dt,
        by = "Sample")

ggplot(sample_libsize_clust_dt,
       aes(x = factor(LibGroup), y = Lib_size, color = condition)) +
  geom_boxplot(varwidth = T) +
  geom_jitter(position = position_dodge2(width = .5), shape = 1)
```

```{r}
datatable(sample_libsize_clust_dt[, .(Nsamples = .N,
                            MaxLibSize = max(Lib_size),
                            MinLibSize = min(Lib_size)), 
                        by = .(LibGroup, condition)][order(LibGroup, condition)],
          rownames = F, filter = "top")
```

# Simulate datasets

## Prepare the source data set 

Select samples of similar library size from the original data set

```{r}
## subset original matrix using samples of similar library size
sample_subset <- sample_libsize_clust_dt[!LibGroup %in% c(3, 4), Sample]
## subset sample metadata 
sample_table <- group_df[sample_subset, "condition", drop = F]

orig_mat <- counts_mt[, sample_subset]

## keep circRNAs expressed in at least a fraction of the samples
min_samples <- floor(ncol(orig_mat) / 2) #3

orig_mat <- orig_mat[rowSums(orig_mat > 0) >= min_samples, ]
```

```{r}
msg <- paste(dim(orig_mat)[1], "circRNAs in", dim(orig_mat)[2], "samples in the fitered original data set.")
print(msg)
```

```{r}
if(Ncircrnas > nrow(orig_mat)){
  msg <- paste("The desired number of circRNAs to be simulated (",  
               Ncircrnas,
               ") exceeds the maximum number of circRNAs available in this data set.",
               nrow(orig_mat),
               "circRNAs will be simulated instead.")
  warning(msg)
}

Ncircrnas <- min(nrow(orig_mat), Ncircrnas) 
```

### Check library size after a first circRNA selection 

```{r}
plot_dt <- 
    merge(data.table(data.frame(LibSize = colSums(orig_mat)), 
                     keep.rownames = "SampleID"), 
          data.table(sample_table, 
                     keep.rownames = "SampleID"), 
          by = "SampleID")

plot_dt$SampleID <- factor(plot_dt$SampleID, levels = plot_dt[order(LibSize), SampleID], ordered = T)

ggplot(plot_dt, 
       aes(x = SampleID, y = LibSize, fill = condition)) +
    geom_col() +
    theme(axis.text.x = element_text(angle = 30, hjust = 1),
          legend.position = "top")
```

```{r}
ggplot(plot_dt, 
       aes(x = condition, y = LibSize, color = condition)) +
    geom_boxplot(varwidth = T, notch = F) +
    geom_point() +
    guides(color = guide_none()) +
    theme(legend.position = "top")
```

`r floor(Ncircrnas * fracDECs)` differentially expressed circRNAs will be simulated.  

### Save the source data set

```{r}
## save source dataset
orig_mat_dge <- edgeR::DGEList(counts = orig_mat, group = sample_table[colnames(orig_mat), "condition"])

qsave(x = orig_mat_dge, 
      file = source_dataset_qs, 
      nthreads = multicoreWorkers(), 
      preset = "fast")
```

The source data sets can be loaded from the <a href="`r source_dataset_qs`">`r source_dataset_qs`</a> R object using the <a href="https://cran.r-project.org/web/packages/qs/index.html">qs</a> package.  

## Set parameters to simulate the data sets

### DE data sets

```{r}
## ---- DE data sets ----
params_list <- 
  list(counts_mt = orig_mat,
       Ncircrnas = Ncircrnas, 
       fracDECs = fracDECs,
       cand_DE_genes = NULL, #nonnull_circs_names,
       group_df = sample_table,
       w = 0.7,
       n.sims = n.sims)

bulk_sims_params <- 
  list(N03_bulk = c(params_list, reps_per_group =  3, model_zeros = FALSE),
       N05_bulk = c(params_list, reps_per_group =  5, model_zeros = FALSE),
       N10_bulk = c(params_list, reps_per_group = 10, model_zeros = FALSE))
```

### Not DE data sets

```{r}
## ---- no DE data sets ----
## use the single condition samples and set fraction of DECs = 0
mock_params_list <- 
  list(counts_mt = orig_mat, #mock_orig_mat,
       Ncircrnas = Ncircrnas, 
       fracDECs = 0,
       cand_DE_genes = NULL,
       group_df = sample_table, #mock_sample_table,
       w = 0.7,
       n.sims = n.sims)

mock_bulk_sims_params <- 
  list(N03_bulk_mock = c(mock_params_list, reps_per_group =  3, model_zeros = FALSE),
       N05_bulk_mock = c(mock_params_list, reps_per_group =  5, model_zeros = FALSE),
       N10_bulk_mock = c(mock_params_list, reps_per_group = 10, model_zeros = FALSE))
```

## Do simulations

```{r}
## do simulations in parallel
ds_par_list <- 
  c(bulk_sims_params,
    mock_bulk_sims_params)

sim_ds_list <-
  bplapply(ds_par_list,
           SPsimSeq_simulate,
           BPPARAM = MulticoreParam(workers = min(length(ds_par_list), 
                                                  multicoreWorkers())))
```

```{r}
qsave(x = sim_ds_list, 
      file = simulated_datasets_qs, 
      nthreads = multicoreWorkers(), 
      preset = "fast")
```

The simulated data sets can be loaded from the <a href="`r simulated_datasets_qs`">`r simulated_datasets_qs`</a> R object using the <a href="https://cran.r-project.org/web/packages/qs/index.html">qs</a> package.  

# Session info

```{r}
sessionInfo()
```

