---
title: "Evaluate benchmark results"
author: "Enrico Gaffo"
date: "`r Sys.Date()`"
output: 
  html_document: 
    toc: yes
    toc_float: yes
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
outdir <- "source_ds_characteristics"
dir.create(path = outdir, showWarnings = F, recursive = T)

knitr::opts_chunk$set(echo = TRUE, 
                      fig.path = file.path(outdir, "Figs/"), 
                      dev = c("png", "svglite", "pdf"))

library(data.table)
library(qs)
library(DT)
library(ComplexHeatmap)
library(scales)
library(ggplot2)
library(ggrepel)
library(ggthemes)
library(patchwork)
library(ggbeeswarm)

library(BiocParallel)

library(edgeR)
```

```{r}
## output file path
dir.create(path = outdir, showWarnings = F, recursive = T)

## input data
ds_names <- c("DM1", "IDC", "IPF", "MS")
unfilt_ds_files <- setNames(paste0("../../data/", 
                                   ds_names, 
                                   "_unfiltered_CirComPara2_circbjr.csv"), 
                            ds_names)

ds_meta_files <- setNames(paste0("../../data/", 
                                 ds_names, 
                                 "_meta.csv"), 
                          ds_names)

trimmed_source_dataset_files <- file.path("..", "simulations", "semiparametric", "simdata",
                                    paste0(ds_names, "_", 
                                    "trimmed_source_dataset.qs"))

names(trimmed_source_dataset_files) <- ds_names

PC_data_file <- "../../data/PMID35078526_rawCIRI2output.tsv"
```

```{r}
nWorkers <- multicoreWorkers()
```

# Data sets characteristics

## Source data sets

```{r}
## read unfiltered data
source_ds_dt <- 
    rbindlist(lapply(unfilt_ds_files,
                     function(x, min_samples = 0){
                         y <- fread(x, data.table = F)
                         m <- as.matrix(y[, -1])
                         rownames(m) <- y[, 1]
                         melt(as.data.table(m[rowSums(m > 0) >= min_samples, ], 
                                            keep.rownames = "circ_id"),
                              id.vars = "circ_id", variable.name = "sample_id")
                     }
    ), 
    idcol = "DS")

source_ds_meta <- 
    rbindlist(lapply(ds_meta_files,
                     fread), 
              idcol = "DS", use.names = T)
```

### CircRNAs per number of samples

Exact number of samples in which a circRNA has been detected.  

```{r, fig.width=6, fig.height=5}
plot.dt <- 
    source_ds_dt[value > 0, 
                 .(n_samples = .N), 
                 by = .(DS, circ_id)][, .(n_circs = .N), 
                                      by = .(DS, n_samples)]

plot.dt[order(-n_samples), cum_circs := cumsum(n_circs), by = .(DS)]

# ggplot(plot.dt,
#        aes(x = factor(n_samples),
#            y = n_circs)) +
#     geom_point(aes(color = DS)) +
#     scale_color_tableau(direction = -1) +
#     facet_wrap(~ DS, scales = "free", ncol = 1) +
#     labs(y = "Number of circRNAs", x = "Number of samples") +
#     theme_classic() +
#     theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

Minimum number of samples in which a circRNA has been detected.  

```{r, fig.width=6, fig.height=5}
# ggplot(plot.dt,
#        aes(x = factor(n_samples), 
#            y = cum_circs)) +
#     geom_point(aes(color = DS)) +
#     scale_color_tableau(direction = -1) +
#     facet_wrap(~ DS, scales = "free", ncol = 1) +
#     labs(y = "Cumulative number of circRNAs", 
#          x = "Cumulative number of samples") + # "(\u2265)"
#     theme_classic() +
#     theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Mean expression per number of samples

```{r, fig.width=6.5, fig.height=8.8}
plot.dt <- 
    merge(source_ds_dt[value > 0, .(n_samples = .N), by = .(DS, circ_id)], 
          source_ds_dt[, .(mean_BJR = mean(value)), by = .(DS, circ_id)], 
          by = c("DS", "circ_id"))
```

```{r, fig.height=8.5, fig.width=3}
bjr_box_plot <-
    ggplot(plot.dt,
           aes(y = factor(n_samples, levels = max(plot.dt$n_samples):1, ordered = T),
               x = mean_BJR, 
               color = DS)) +
    geom_boxplot(outlier.size = .3, #outlier.alpha = .5,
                 outlier.shape = NA, # this removes the outliers
                 varwidth = F, 
                 notch = F, position = position_dodge2(preserve = "single")) +
    scale_x_log10(label = label_comma(accuracy = 1)) +
    scale_color_tableau(direction = -1) +
    # facet_wrap(~ DS, scales = "fixed", nrow = 1) +
    labs(x = "Mean BJR", y = "Number of samples") +
    theme_bw() +
    theme(legend.position = "none",
        axis.text.x = element_text(angle = 90,
                                     hjust = 1,
                                     vjust = .5),
          panel.grid.minor.y = element_blank(),
          panel.grid.major.y = element_blank(),
          panel.grid.minor.x = element_blank(),
          panel.spacing = unit(.1, "lines"))

ncircs_plot <-
    ggplot(plot.dt[, .(n_circs = .N), by = .(DS, n_samples)],
           aes(x = factor(n_samples, levels = max(plot.dt$n_samples):1, ordered = T), 
               y = n_circs, 
               # fill = DS, 
               color = DS)) +
    # geom_col(position = position_dodge2(preserve = "single")) +
    geom_line(aes(group = DS)) +
    scale_color_tableau(name = "Dataset", direction = -1) +
    geom_point() +
    coord_flip() +
    scale_y_continuous("Number of\ncircRNAs") +
    # scale_y_sqrt("Number of\ncircRNAs") +
    # scale_y_log10("Number of\ncircRNAs") +
    theme_bw() +
    theme(legend.position = c(.65, .2),
          legend.background = element_blank(),
        axis.text.x = element_text(angle = 90,
                                     hjust = 1,
                                     vjust = .5),
          panel.grid.minor.y = element_blank(),
          panel.grid.major.y = element_blank(),
          panel.grid.minor.x = element_blank(), 
          panel.spacing = unit(.1, "lines"))

wrap_plots(bjr_box_plot +
               theme(plot.margin = margin(0, 0, 0, 0)), 
           ncircs_plot + 
               labs(x = NULL) +
               # guides(color = "none") +
               theme(axis.text.y = element_blank(),
                     axis.ticks.y = element_blank(), 
                     plot.background = element_blank(),
                     plot.margin = margin(0, 0, 0, 0)), 
           # guides = "collect", 
           nrow = 1, 
           widths = c(.6, .4)) &
    # scale_color_tableau(name = "Study", direction = -1) &
    theme(#legend.position = "top", 
          text = element_text(size = 10))
```

### Unfiltered data sets {.tabset}

#### BJR proportion 

```{r, fig.width=4, fig.height=3.5}
source_hist_cnt <- 
    source_ds_dt[, .(histBJR = .N), 
             by = .(DS, BJR = value)][, Frac := histBJR / sum(histBJR), 
                                  by = .(DS)][]
plot_dt <- source_hist_cnt[, .(AvgFrac = mean(Frac)),
                    by = .(DS, BJR)]

ds_stats <- 
    source_ds_dt[, .(nSamples = .N), 
                 by = .(DS, circ_id)][, .(nSamples = head(nSamples, 1),
                                          nCircs = .N), by = DS]

ch_p <- 
    ggplot(plot_dt, aes(x = BJR, y = AvgFrac)) + 
    geom_col(position = "identity", alpha = 1, aes(fill = DS)) +
    # facet_wrap(facets = ~ DS, ncol = 1, scales = "free_y") +
    facet_grid(rows = vars(DS)) +
    coord_cartesian(xlim = c(0, 15)) +
    geom_label(data = ds_stats, 
               size = 3,
               aes(x = 5, y = .5, 
                   label = paste("# samples:", nSamples, "\n# circRNAs:", comma(nCircs))), hjust = 0) +
    labs(x = "Backsplice-junction reads") +
    scale_y_continuous("Count matrix fraction (%)", 
                       labels = function(x)round(as.numeric(x)*100)) + #labels = percent
    scale_x_continuous(breaks = 0:15, 
                       labels = 0:15) +
    scale_fill_tableau(direction = -1) +
    theme_bw() +
    theme(legend.position = "none", 
          axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5), 
          plot.margin = unit(x = c(.1, .1, .1, .1), units = "lines"), 
          strip.text = element_blank(), 
          panel.grid.major.x = element_blank(),
          panel.grid.minor = element_blank(),
          strip.background = element_blank())

ls_bxp <- 
    ggplot(source_ds_dt[, .(LibSize = sum(value)), by = .(DS, sample_id)],
           aes(x = "", y = LibSize)) +
    geom_boxplot(varwidth = T,
                 notch = F,
                 outlier.size = .5,
                 aes(color = DS)) + #, outlier.shape = NA
    # geom_quasirandom(groupOnX = T, varwidth = T, alpha = .5, aes(fill = LibSize), shape = 21) +
    # geom_violin(aes(color = DS), 
    #             trim = T, 
    #             draw_quantiles = c(.25, .5, .75)) +
    # scale_fill_viridis_c() +
    scale_x_discrete(name = NULL) +
    scale_y_log10(labels = function(x)sub("000$", "K", x)) +
    scale_color_tableau(direction = -1) +
    labs(x = NULL, y = "Library size") +
    coord_flip() +
    # facet_wrap(facets = ~ DS, ncol = 1) + #, scales = "free_x"
    facet_grid(rows = vars(DS)) +
    theme_bw() +
    theme(legend.position = "none",
          axis.ticks.y = element_blank(), 
          panel.grid.major.y = element_blank(),
          plot.margin = unit(x = c(.1, .1, .1, .1), units = "lines"))

ch_p + ls_bxp +
    plot_layout(widths = c(3, 1))
```

#### Sparsity

Sparsity for each sample is calculated counting the circRNAs with zero count that have been detected in other samples of the same data set.  

```{r, fig.width=3.5, fig.height=2.5}
plot_dt <- 
    merge(merge(source_ds_dt[, .(Sparsity = sum(value == 0)/length(value)), 
                             by = .(DS, sample_id)],
                source_ds_dt[, .(LibSize = sum(value)), 
                             by = .(DS, sample_id)], 
                by = c("DS", "sample_id")),
          source_ds_dt[, .N, by = .(DS, circ_id)][, .(Features = .N), by = DS],
          by = "DS")

# ggplot(plot_dt, 
#        aes(x = LibSize, y = Sparsity * 100, color = DS)) +
#     geom_point(alpha = .5, size = 2) +
#     geom_smooth(method = "glm", 
#                 # group = 1, 
#                 # color = "black", 
#                 linetype = "dashed", 
#                 se = F) +
#     scale_x_continuous("Library size (BJRs)", labels = comma) +
#     scale_y_continuous("Sparsity (%)", limits = c(0, 100)) +
#     scale_color_tableau(name = "Dataset", direction = -1) +
#     # scale_size(name = "CircRNAs", breaks = sort(plot_dt$Features)) +
#     guides(color = guide_legend(nrow = 1, 
#                                 title.position = "top", 
#                                 title.hjust = .5)) +
#     theme_bw() +
#     theme(legend.position = c(.5, .175), 
#           legend.background = element_rect(colour = "grey55"),
#           legend.margin = margin(t = .1, r = .2, b = .1, l = .2, unit = "lines"),
#           panel.grid.minor = element_blank())
```

Below, sparsity is calculated counting the fraction of zeros in the data set matrix.  
Mean library size is the mean sum of BJRs in each sample of the data set.  

```{r, fig.width=4.5, fig.height=2.5}
plot_dt <- 
    merge(merge(source_ds_dt[, .(Sparsity = sum(value == 0)/length(value)), by = DS],
                source_ds_dt[, .(LibSize = sum(value)), 
                             by = .(DS, sample_id)][, .(`Mean library size` = mean(LibSize)), 
                                                    by = DS], 
                by = "DS"),
          source_ds_dt[, .N, by = .(DS, circ_id)][, .(Features = .N), by = DS],
          by = "DS")

cortest <- cor.test(x = plot_dt$`Mean library size`, y = plot_dt$Sparsity, method = "pearson")

# cortest$p.value
cortest$estimate
```


```{r, fig.width=4.5, fig.height=2.5}
ggplot(plot_dt, 
       aes(x = `Mean library size`, y = Sparsity * 100, color = DS)) +
    geom_smooth(method = "glm", group = 1, color = "black", linetype = "dashed", se = T) +
    geom_point(aes(size = Features)) +
    geom_label_repel(aes(label = DS), show.legend = F) +
    annotate(geom = "label", x = 25000, y = 25, 
             label = paste0("P=", 
                           round(cortest$p.value, 2),
                           ", r=",
                           round(cortest$estimate, 2))) +
    # scale_x_log10() +
    scale_x_continuous(labels = comma) +
    scale_y_continuous("Sparsity (%)", limits = c(0, 100)) +
    scale_color_tableau(direction = -1) +
    scale_size(name = "CircRNAs", breaks = sort(plot_dt$Features)) +
    guides(color = "none") +
    theme_bw() +
    theme(legend.position = "right",
          panel.grid.minor = element_blank())
```

```{r}
datatable(plot_dt)
```

### 3 samples filter {.tabset}

Data sets after filtering according to circRNAs detected in 3 or more samples.  

#### Within condition correlation of samples

Original data sets after sample selection and circRNA preliminary filters.  

```{r}
trimmed_source_dataset_l <- lapply(trimmed_source_dataset_files, qread)

within_cond_corr <- function(ds, cor.meth = "pearson"){
    
    g1 <- rownames(ds$samples)[as.integer(ds$samples$group) == 1]
    g2 <- rownames(ds$samples)[as.integer(ds$samples$group) == 2]
    
    cor_g1 <- cor(x = ds$counts[, g1], method = cor.meth)
    cor_g2 <- cor(x = ds$counts[, g2], method = cor.meth)
    
    list(G1_cor = cor_g1[upper.tri(cor_g1)],
      G2_cor = cor_g2[upper.tri(cor_g2)])
}

# data.frame(lapply(trimmed_source_dataset_l, within_cond_corr, cor.meth = "pearson"))
cor_lists <- sapply(trimmed_source_dataset_l, within_cond_corr, cor.meth = "pearson", simplify = F)
cor_dt <- rbindlist(lapply(cor_lists, function(x)rbind(data.table(Group = "G1", CorPear = x[[1]]),
                                   data.table(Group = "G2", CorPear = x[[2]]))), 
          idcol = "DS")
```

```{r}
datatable(cor_dt, rownames = F, filter = "top")
```

```{r}
datatable(cor_dt[, .(Min = min(CorPear), Max = max(CorPear)), by = .(DS, Group)])
```

#### 3S filter BJR proportion 

```{r, fig.width=4, fig.height=3.5}
circ_id3s <- source_ds_dt[value > 0, .N, by = .(DS, circ_id)][N > 2, circ_id]

source_hist_cnt <- 
    source_ds_dt[circ_id %in% circ_id3s, 
                 .(histBJR = .N), 
             by = .(DS, BJR = value)][, Frac := histBJR / sum(histBJR), 
                                  by = .(DS)][]
plot_dt <- source_hist_cnt[, .(AvgFrac = mean(Frac)),
                    by = .(DS, BJR)]

ds_stats <- 
    source_ds_dt[circ_id %in% circ_id3s, 
                 .(nSamples = .N), 
                 by = .(DS, circ_id)][, .(nSamples = head(nSamples, 1),
                                          nCircs = .N), by = DS]

ch_p <- 
    ggplot(plot_dt, aes(x = BJR, y = AvgFrac)) + 
    geom_col(position = "identity", alpha = 1, aes(fill = DS)) +
    # facet_wrap(facets = ~ DS, ncol = 1, scales = "free_y") +
    facet_grid(rows = vars(DS)) +
    coord_cartesian(xlim = c(0, 15)) +
    geom_label(data = ds_stats, 
               size = 3,
               aes(x = 5, y = .5, 
                   label = paste("# samples:", nSamples, "\n# circRNAs:", comma(nCircs))), hjust = 0) +
    labs(x = "Backsplice-junction reads") +
    scale_y_continuous("Count matrix fraction (%)", 
                       labels = function(x)round(as.numeric(x)*100)) + #labels = percent
    scale_x_continuous(breaks = 0:15, 
                       labels = 0:15) +
    scale_fill_tableau(direction = -1) +
    theme_bw() +
    theme(legend.position = "none", 
          axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5), 
          plot.margin = unit(x = c(.1, .1, .1, .1), units = "lines"), 
          strip.text = element_blank(), 
          panel.grid.major.x = element_blank(),
          panel.grid.minor = element_blank(),
          strip.background = element_blank())

ls_bxp <- 
    ggplot(source_ds_dt[, .(LibSize = sum(value)), by = .(DS, sample_id)],
           aes(x = "", y = LibSize)) +
    geom_boxplot(varwidth = T,
                 notch = F,
                 outlier.size = .5,
                 aes(color = DS)) + #, outlier.shape = NA
    # geom_quasirandom(groupOnX = T, varwidth = T, alpha = .5, aes(fill = LibSize), shape = 21) +
    # geom_violin(aes(color = DS), 
    #             trim = T, 
    #             draw_quantiles = c(.25, .5, .75)) +
    # scale_fill_viridis_c() +
    scale_x_discrete(name = NULL) +
    scale_y_log10(labels = function(x)sub("000$", "K", x)) +
    scale_color_tableau(direction = -1) +
    labs(x = NULL, y = "Library size") +
    coord_flip() +
    # facet_wrap(facets = ~ DS, ncol = 1) + #, scales = "free_x"
    facet_grid(rows = vars(DS)) +
    theme_bw() +
    theme(legend.position = "none",
          axis.ticks.y = element_blank(), 
          panel.grid.major.y = element_blank(),
          plot.margin = unit(x = c(.1, .1, .1, .1), units = "lines"))

ch_p + ls_bxp +
    plot_layout(widths = c(3, 1))
```

#### Sparsity

Data sets after filtering according to circRNAs detected in 3 or more samples.  

```{r, fig.width=4.5, fig.height=2.5}
plot_dt <- 
    merge(merge(source_ds_dt[circ_id %in% circ_id3s,
                             .(Sparsity = sum(value == 0)/length(value)), by = DS],
                source_ds_dt[circ_id %in% circ_id3s, 
                             .(LibSize = sum(value)), 
                             by = .(DS, sample_id)][, .(`Mean library size` = mean(LibSize)), 
                                                    by = DS], 
                by = "DS"),
          source_ds_dt[circ_id %in% circ_id3s, 
                       .N, by = .(DS, circ_id)][, .(Features = .N), by = DS],
          by = "DS")

cortest <- cor.test(x = plot_dt$`Mean library size`, y = plot_dt$Sparsity, method = "pearson")

# cortest$p.value
cortest$estimate

ggplot(plot_dt, 
       aes(x = `Mean library size`, y = Sparsity * 100, color = DS)) +
    geom_smooth(method = "glm", group = 1, color = "black", linetype = "dashed", se = T) +
    geom_point(aes(size = Features)) +
    geom_label_repel(aes(label = DS), show.legend = F) +
    annotate(geom = "label", x = 25000, y = 25, 
             label = paste0("P=", 
                           round(cortest$p.value, 2),
                           ", r=",
                           round(cortest$estimate, 2))) +
    # scale_x_log10() +
    scale_x_continuous(labels = comma) +
    scale_y_continuous("Sparsity (%)", limits = c(0, 100)) +
    scale_color_tableau(direction = -1) +
    scale_size(name = "CircRNAs", breaks = sort(plot_dt$Features)) +
    guides(color = "none") +
    theme_bw() +
    theme(legend.position = "right",
          panel.grid.minor = element_blank())
```

```{r}
datatable(plot_dt)
```

### PCAs {.tabset}

```{r}
# x <- source_ds_dt[circ_id %in% circ_id3s]
# y <- source_ds_meta
# dsname <- "DM1"

plot_pca <- function(dsname, x, y){
    counts <- as.matrix(data.frame(dcast(data = x[DS == dsname], 
                                         formula = circ_id ~ sample_id, 
                                         value.var = "value"), 
                                   row.names = "circ_id"))
    
    sampleTable <- data.frame(y[DS == dsname, .(sample_id, Group = condition)], 
                              row.names = "sample_id")
    
    
    dge <- edgeR::DGEList(counts = counts[, rownames(sampleTable)], group = sampleTable$Group)
    dge <- edgeR::calcNormFactors(dge, method = "TMM")
    cpms <- edgeR::cpm(dge, log = T, prior.count = 1)
    
    pcs <- prcomp(x = t(cpms), scale. = F, center = T)
    var.props <- summary(pcs)$importance[2, ]
    df <- cbind(sampleTable, pcs$x)
    
    ggplot2::ggplot(df, aes(x = PC1, y = PC2, color = Group)) +
        geom_point() +
        labs(x = paste("PC1:", percent(var.props[1])),
             y = paste("PC2:", percent(var.props[2]))) +
        theme_bw()
}
```

```{r}
# source_ds_meta[, .N, by = .(condition)]
source_ds_meta[grepl("normal|control", condition, ignore.case = T), condition := "Normal"]
```

#### DM1

```{r, fig.width=4.5, fig.height=3.5}
plot_pca(dsname = "DM1", x = source_ds_dt[circ_id %in% circ_id3s], y = source_ds_meta) +
    coord_fixed(ratio = 1) +
    theme(legend.position = "top")
```

#### IDC

```{r, fig.width=4.5, fig.height=4.5}
plot_pca(dsname = "IDC", x = source_ds_dt[circ_id %in% circ_id3s], y = source_ds_meta) +
    coord_fixed(ratio = 1) +
    theme(legend.position = "top")
```

#### IPF

```{r, fig.width=4.5, fig.height=4.5}
plot_pca(dsname = "IPF", x = source_ds_dt[circ_id %in% circ_id3s], y = source_ds_meta) +
    coord_fixed(ratio = 1) +
    theme(legend.position = "top")
```

#### MS

```{r, fig.width=4.5, fig.height=4.5}
plot_pca(dsname = "MS", x = source_ds_dt[circ_id %in% circ_id3s], y = source_ds_meta) +
    coord_fixed(ratio = 1) +
    theme(legend.position = "top")
```

### PC data set {.tabset}

```{r}
counts_dt <- fread(PC_data_file,
                   data.table = T,
                   showProgress = F,
                   drop = c("chr", "start", "end", "strand", "gene_id", "circRNA_type"))

## filter the original dataset
counts_dt_m <- melt(counts_dt,
                    id.vars = "circRNA_ID",
                    variable.name = "sample_id",
                    value.name = "BJR")
counts_dt_m[, c("ID", "Group") := tstrsplit(sample_id, "_"), by = sample_id]

## keep only circRNAs expressed in > 2 samples per condition
keep <- counts_dt_m[BJR > 0, .N,
                    by = .(circRNA_ID, Group)][N > 2 &
                                                   Group != "MPC", unique(circRNA_ID)]

## read sample groups
sampleTable <- data.frame(unique(counts_dt_m[Group != "MPC",
                                             .(sample_id, Group)][order(Group, sample_id)]),
                          row.names = "sample_id")

counts <-
    as.matrix(data.frame(counts_dt, check.names = F,
                         row.names = "circRNA_ID"))[keep, rownames(sampleTable)]
# dim(counts)

## check possible biases

dge <- DGEList(counts = counts[, rownames(sampleTable)], group = sampleTable$Group)
dge <- calcNormFactors(dge, method = "TMM")
cpms <- cpm(dge, log = T, prior.count = 1)

pcs <- prcomp(x = t(cpms), scale. = F, center = T)
var.props <- summary(pcs)$importance[2, ]
df <- cbind(sampleTable, pcs$x)
```

#### PCA

```{r, fig.width=4.5, fig.height=3.5}

ggplot2::ggplot(df, aes(x = PC1, y = PC2, color = Group)) +
    geom_point(alpha = .7) +
    scale_color_discrete(labels = c("Normal", "Prostate Cancer"), direction = -1) +
    geom_rect(aes(xmin = -40, xmax = 50, ymin = -30, ymax = 0), 
              fill = NA, 
              color = "red") + 
    annotate(geom = "text", x = 25, y = -5, label = "Batch 2", color = "red") +
    labs(x = paste("PC1:", percent(var.props[1])),
         y = paste("PC2:", percent(var.props[2]))) +
    theme_bw() +
    coord_fixed(ratio = 1) +
    theme(legend.position = "top")
```


```{r}
df$Batch <- ifelse(df$PC2 > 0, "B1", "B2")
sampleTable$Batch <- df[rownames(sampleTable), "Batch"]
## get batch-group sample sizes
table(sampleTable[, c("Batch", "Group")])
```

#### Batch 2

```{r}
## keep only samples from the largest batch
st <- sampleTable[sampleTable$Batch == "B2", "Group", drop = F]
ct <- counts[, rownames(st)]
ct <- ct[rowSums(ct > 0) > 2, ]
dim(ct)

dge.b2 <- DGEList(counts = ct, group = st$Group)
dge.b2 <- calcNormFactors(dge.b2, method = "TMM")
cpms.b2 <- cpm(dge.b2, log = T, prior.count = 1)

pcs.b2 <- prcomp(x = t(cpms.b2), scale. = F, center = T)
var.props.b2 <- summary(pcs.b2)$importance[2, ]
df.b2 <- cbind(st, pcs.b2$x)
```


```{r, fig.width=4.5, fig.height=3.5}
ggplot2::ggplot(df.b2, aes(x = PC1, y = PC2, color = Group)) +
        geom_point() +
        labs(x = paste("PC1:", percent(var.props.b2[1])),
             y = paste("PC2:", percent(var.props.b2[2]))) + 
    scale_color_discrete(labels = c("Normal", "Prostate Cancer"), direction = -1) +
    ggtitle("Batch 2") +
    theme_bw() +
    coord_fixed(ratio = 1) +
    theme(legend.position = "top", plot.title = element_text(hjust = .5))
```

```{r}
pc_cor_g1 <- cor(ct[, rownames(st)[st$Group == "AN"]])
pc_cor_g2 <- cor(ct[, rownames(st)[st$Group == "T"]])

# paste("AN Pearson mean cor =", mean(cor_g1))
# paste("T Pearson mean cor =", mean(cor_g2))
```


```{r}
pc_cor_dt <- rbind(data.table(Group = "G1", CorPear = pc_cor_g1[upper.tri(pc_cor_g1)]),
                   data.table(Group = "G2", CorPear = pc_cor_g2[upper.tri(pc_cor_g2)]))
datatable(pc_cor_dt, rownames = F, filter = "top")
```

```{r}
pc_cor_dt[, .(Min = min(CorPear), Max = max(CorPear)), by = .(Group)]
```

```{r}
datatable(data.table(st, keep.rownames = "Sample"), 
          filter = "top", rownames = F,
          caption = "Batch 2 samples")
```

#### BJR

```{r, fig.width=4, fig.height=2.5}
PC_ds_dt <- data.table(melt(dge.b2$counts))
PC_hist_cnt <- PC_ds_dt[, .(histBJR = .N), 
                        by = .(BJR = value)][, Frac := histBJR / sum(histBJR)][]
plot_dt <- PC_hist_cnt[, .(AvgFrac = mean(Frac)),
                    by = .(BJR)]

PC_ds_stats <- data.table(nSamples = length(unique(PC_ds_dt$Var2)), 
                          nCircs = length(unique(PC_ds_dt$Var1)))

ch_p <- 
    ggplot(plot_dt, aes(x = BJR, y = AvgFrac)) + 
    geom_col(position = "identity", alpha = 1) +
    # facet_wrap(facets = ~ DS, ncol = 1, scales = "free_y") +
    # facet_grid(rows = vars(DS)) +
    coord_cartesian(xlim = c(0, 15)) +
    geom_label(data = PC_ds_stats, 
               size = 3,
               aes(x = 5, y = .5, 
                   label = paste("# samples:", nSamples, "\n# circRNAs:", comma(nCircs))), hjust = 0) +
    labs(x = "Backsplice-junction reads") +
    scale_y_continuous("Count matrix fraction (%)", 
                       labels = function(x)round(as.numeric(x)*100)) + #labels = percent
    scale_x_continuous(breaks = 0:15, 
                       labels = 0:15) +
    scale_fill_tableau(direction = -1) +
    theme_bw() +
    theme(legend.position = "none", 
          axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5), 
          plot.margin = unit(x = c(.1, .1, .1, .1), units = "lines"), 
          strip.text = element_blank(), 
          panel.grid.major.x = element_blank(),
          panel.grid.minor = element_blank(),
          strip.background = element_blank())

ls_bxp <- 
    ggplot(PC_ds_dt[, .(LibSize = sum(value)), by = .(Var2)],
           aes(x = "", y = LibSize)) +
    geom_boxplot(varwidth = T,
                 notch = F,
                 outlier.size = .5) + #, outlier.shape = NA
    # geom_quasirandom(groupOnX = T, varwidth = T, alpha = .5, aes(fill = LibSize), shape = 21) +
    # geom_violin(aes(color = DS), 
    #             trim = T, 
    #             draw_quantiles = c(.25, .5, .75)) +
    # scale_fill_viridis_c() +
    scale_x_discrete(name = NULL) +
    scale_y_log10(labels = function(x)sub("000$", "K", x)) +
    scale_color_tableau(direction = -1) +
    labs(x = NULL, y = "Library size") +
    coord_flip() +
    # facet_wrap(facets = ~ DS, ncol = 1) + #, scales = "free_x"
    # facet_grid(rows = vars(DS)) +
    theme_bw() +
    theme(legend.position = "none",
          axis.ticks.y = element_blank(), 
          panel.grid.major.y = element_blank(),
          plot.margin = unit(x = c(.1, .1, .1, .1), units = "lines"))

ch_p + ls_bxp +
    plot_layout(widths = c(3, 1))
```

# Session info

```{r}
sessionInfo()
```

